Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-13 doc/JFLA2022/paper.tex
clarify that gaia fix was anonymous

The Gaia project by Jos\'e Grimm aimed to formalize mathematics in the style of by N. Bourbaki in Coq. The formalization of the first book by Bourbaki, on the theory of sets, was initially described in a technical report in July 2009~\cite{Grimm2009a}. Grimm then wrote (and continually updated) technical reports describing the formalization of Bourbaki's two subsequent books~\cite{Grimm2009b,Grimm2016} and additional topics in number theory~\cite{grimm:hal-00911710,Grimm2014}, before he passed away in 2019.

In 2020, members of \community transferred the Gaia source code to GitHub and adapted it for recent releases of the Mathematical Components library, which Gaia heavily relies on. Volunteers (``collaborators of Nicolas Bourbaki'') then finished the only in-progress proof left by Grimm. At around 165,000 lines of code, Gaia is currently one of the largest maintained open source Coq projects~\cite{Gaia}.

>>>>

The Gaia project by Jos\'e Grimm aimed to formalize mathematics in the style of N. Bourbaki in Coq. The formalization of the first book by Bourbaki, on the theory of sets, was initially described in a technical report in July 2009~\cite{Grimm2009a}. Grimm then wrote (and continually updated) technical reports describing the formalization of Bourbaki's two subsequent books~\cite{Grimm2009b,Grimm2016} and additional topics in number theory~\cite{grimm:hal-00911710,Grimm2014}, before he passed away in 2019.

In 2020, members of \community transferred the Gaia source code to GitHub and adapted it for recent releases of the Mathematical Components library, which Gaia heavily relies on. Anonymous volunteers (``collaborators of Nicolas Bourbaki'') then finished the only in-progress proof left by Grimm. At around 165,000 lines of code, Gaia is currently one of the largest maintained open source Coq projects~\cite{Gaia}.
